---
title: "Galiano BioBlitz 2023 outcomes: vascular plants"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("scripts/loadData.R")
```

## Community science contributions

Members of the Hunterston Farm community have documented a total of `r nrow(summary)` vascular plant species since 2010, through the combined efforts of `r length(unique(records$recordedBy))` individuals. During the recent 2023 BioBlitz at Hunterston Farms, participants confirmed `r round((nrow(confirmed)/(nrow(confirmed)+nrow(reported))*100), digits = 0)` percent of the historically reported plant diversity and added `r nrow(new)` new species to the list. Of the `r nrow(reported)+nrow(confirmed)` reported species, `r nrow(reported)` species remained undetected after these recent search efforts, having not been observed since 2010.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("scripts/Plot_script.R")
stacked_bar_plot
```

## Authors

Antranig Basman, Andrew Simon

November 11th, 2024

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
