---
title: "Galiano Bioblitz 2023 outcomes: vascular plants"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
records <- read.csv("tabular_data/Galiano_Island_vascular_plant_records_consolidated-prepared.csv")
summary <- read.csv("tabular_data/Galiano_Tracheophyta_review_summary_reviewed_2024-10-07-assigned_revised.csv")
new <- summary %>% filter(str_detect(Reporting.Status, "new")) 
confirmed <- summary %>% filter(Reporting.Status == 'confirmed') 
reported <- summary %>% filter(Reporting.Status == 'reported') 
observed <- summary %>% filter(Observation == 'observed') 
```

## Community science contributions

Through the combined efforts of `r length(unique(records$recordedBy))` individuals, 
the Hunterston Farms naturalist community has now documented a total of `r nrow(summary)` 
vascular plant species. Based on search efforts over the last 
decade, `r round((nrow(confirmed)/(nrow(confirmed)+nrow(reported))*100), digits = 0)` 
percent of the historically reported plant diversity has been confirmed and `r nrow(new)` new species 
reports added to the list. Community members have now 
documented `r round((nrow(observed)/(nrow(summary))*100), digits = 0)` percent of the 
plant diversity known to the region on iNaturalist.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("scripts/Plot_script.R")
reportingStatusFig
```

## Authors

Antranig Basman, Andrew Simon

November 11th, 2024

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
