---
title: "Galiano BioBlitz 2023 outcomes: vascular plants"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs") })
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("scripts/loadData.R")
```

## Community science contributions

Through the combined efforts of `r length(unique(records$recordedBy))` individuals, 
the Hunterston Farms naturalist community has now documented a total of `r nrow(summary)` 
vascular plant species. Based on search efforts over the last 
decade, `r round((nrow(confirmed)/(nrow(confirmed)+nrow(reported))*100), digits = 0)` 
percent of the historically reported plant diversity has been confirmed and `r nrow(new)` new species 
reports added to the list. Community members have now 
documented `r round((nrow(observed)/(nrow(summary))*100), digits = 0)` percent of the 
plant diversity known to the region on iNaturalist.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("scripts/Plot_script.R")
reportingStatusFig
```

## Authors

Antranig Basman, Andrew Simon

November 11th, 2024

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
